### 2019-01-09 Sections/costs_and_attributes_in_quantum_networks.tex
doing another save

The \textit{classical mutual information}\index{Classical channel capacity} of channel $\mathcal{E}$ is defined as,
\begin{align}\index{mutinfoclassical}
I(\mathcal{E}) = \max_{p(x)} I(X;Y)
% 
\end{align}
with the intuitive interpretation as the maximum mutual information between input and output states that can be achieved for the channel.  For a noisy channel, if the input contains product states (i.e. entanglement between input states is not allowed), the classical capacity can be expressed as
\begin{align}
\chi(\mathcal{E}) = \max_{p_i,\rho_i} S(\rho) - \sum_i p_i S(\rho_i) \label{eq:holevoinfo}
\end{align}

@@

A summary of the different measure of classical and quantum capacities are given in Table \ref{tab:capacitie}.
\begin{widetext}
\begin{table}[hbt]
\begin{tabular}{ |c | c | c| c| } \hline
Capacity & Type of information & Correlation measure &Capacity formula  \\ \hline
Classical &Classical information &Holevo information &Eq.~\eqref{eq:holevoinfo}       \\
Entanglement Assisted Classical & Classical information & Quantum mutual information &Bennett-Shor-Smolin-Thapliyal formula \\
Quantum &Quantum information &Quantum Coherent Information &Eq\eqref{eq:quantcohinfo} \\ \hline
\end{tabular}
\caption{\label{tab:capacitie} Measure of classical and quantum channel capacities.}
\end{table}
\end{widetext}

>>>>

The \textit{classical mutual information}\index{Classical channel capacity} of channel $\mathcal{E}$ is defined as,
\begin{align}\index{mutinfoclassical}
I(\mathcal{E}) = \max_{p(x)} I(X;Y)
% 
\end{align}
with the intuitive interpretation as the maximum mutual information between input and output states that can be achieved for the channel.  For a noisy channel, if the input contains product states (i.e. entanglement between input states is not allowed), the classical capacity can be expressed as
\begin{align}
\chi(\mathcal{E}) = \max_{p_i,\rho_i} S(\rho) - \sum_i p_i S(\rho_i) \label{eq:holevoinfo}
\end{align}
\noindent which is known as the Holevo bound.

@@

For a more in-depth discussion of channel capacities

% A summary of the different measure of classical and quantum capacities are given in Table \ref{tab:capacitie}.
% \begin{widetext}
% \begin{table}[hbt]
% \begin{tabular}{ |c | c | c| c| } \hline
% Capacity & Type of information & Correlation measure &Capacity formula  \\ \hline
% Classical &Classical information &Holevo information &Eq.~\eqref{eq:holevoinfo}       \\
% % Entanglement Assisted Classical & Classical information & Quantum mutual information &Bennett-Shor-Smolin-Thapliyal formula \\
% Quantum &Quantum information &Quantum Coherent Information &Eq\eqref{eq:quantcohinfo} \\ \hline
% \end{tabular}
% \caption{\label{tab:capacitie} Measure of classical and quantum channel capacities.}
% \end{table}
% \end{widetext}
